GNSS-based \textcolor{r_s}{Short-term} Displacement Detection Using Bayesian Inference for Deformation Monitoring

### 2021-09-12 paper/r1/manuscript-mssp.tex
add ndop_snrmp_analysis

		\title{GNSS-based Displacement Detection Using Bayesian Inference for Deformation Monitoring}

@@

	\label{intro}
	%全球定位系统系统的应用-》位移探测
	%在自然灾害监测，或者工业测量等领域，GNSS被用于位移探测。
	%传统测量仪器的弊端，GNSS位移探测的优势。
	%GNSS在位移探测中扮演的角色，以及位移探测的要求
	%目前人们对于基于GNSS位移探测的研究更过的关注与如何提高定位的精度，而忽略了如何从GNSS获取的坐标序列中识别并提取位移。
	In recent decades, the Global navigation satellite system (GNSS) has been widely used in surveying, civil aviation, and autonomous vehicle as a positioning method\cite{barry2011surveying,iatsouk2004development}. 
	Besides, as a displacement detection method in deformation monitoring, GNSS has been widely applied to engineering fields such as landslide monitoring\cite{awange2012environmental}, subsidence survey\cite{bian2014monitoring}, industrial measurement\cite{pavasovic2011application}. 
	Displacement is an important parameter in engineering analysis in structural mechanics and geomechanics\cite{TASORA2020112635,BIGONI2020113315}.
	Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high precision, and weather independence\cite{shen2019a}. 
	%随着物联网通信技术标准的制订和创新，高精度定位技术，例如RTK，PPP，以及GNSS传输协议NTRIP的发展，GNSS定位结果可以被实时传输到云端。
	With the development of the Internet of things (IoT), GNSS high-precision positioning technology, and GNSS enhanced information transmission protocol, high-precision GNSS positioning results can be transmitted to the cloud in real-time.
	%Displacement detection involves displacement identification and extraction. 
	GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results\cite{abidin2004use,rs12203375}. 
	There are many researches on displacement detection based on GNSS, which can be divided into two categories.

@@

	\textcolor{r_s}{
	The other category is about displacement detection research based on GNSS.
	There are many studies on the use of high-rate GNSS for structure displacement extraction and parameter identification.
	Psimoulis et al.\cite{psimoulis2008_1,psimoulis2008_2} studied the feasibility of using GNSS for structural vibration detection. Experiments were carried out to evaluate the use of Global positioning system (GPS) to determine the parameters of oscillation of major structures.
	Meng et al.\cite{Meng_2018} presented the challenges faced by the design and implementation of a new monitoring system for large bridges. Damage detection in SHM of long-span bridges is very challenging because there is no general damage definition, and damage is usually unique and bridge-specific. Psimoulis et al.\cite{psimoulis2018detection} presented an algorithm named RT-SHAKE to detect ground motions, which aims to detect seismic motion more sensitively and robustly.	There are also studies on the relationship between receiver parameters and high-rate GNSS measurement\cite{Hberling2015,Moschas2015}.
	H{\"a}berling et al.\cite{Hberling2015} argued that due to the large error of dynamic GNSS measurement if high-rate GNSS is to be a valuable tool for seismic displacement measurement above 1 Hz, the baseband parameters of the GNSS receiver must be considered.
	Moschas et al.\cite{Moschas2015} studied the relationship between the phase-locked loop(PLL) bandwidth and noise in 100 Hz GPS measurement.
	The results show that the measurement correlation decreases with the increase of PLL bandwidth from low to high to 100 Hz. Shen et al.\cite{shennan_2019} gave a more detailed review of dynamic structural health monitoring technology based on GNSS. There are also studies on displacement detection such as landslide, and GNSS is usually used as a static positioning method.}
	Gili et al.\cite{gili2000using} was one of the first landslide monitoring studies using GNSS technology, in which traditional measurement data were used as a comparison. 
	The results showed that the accuracy of the GPS measurement over a period of 26 months was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
	A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\cite{rs12203375}. 
	The results of a nine-month of field monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement was obtained by the direct difference between the coordinates of the start and end periods.
	In addition, GNSS was also combined with synthetic aperture radar technology for displacement detection, in which long-term GNSS measurements were used as references\cite{atanasova2018ground,fuhrmann2015estimation}.
	In these studies, the GNSS static positioning mode is usually adopted.

	%目前针对GNSS动态定位时间序列的位移识别和提取的研究还很少。目前研究都是基于长周期时间序列进行分析，对于动态定位结果分析的研究还是有限。
	At present, there are few studies on displacement identification and extraction of GNSS kinematic positioning time series. In \cite{li2010deformation}, a multiple Kalman filters model was proposed for deformation detection in the GPS real-time series. Different filters in the model represent different displacement models, which need to be defined in advance. 
	In addition, the index-based is also widely used, but it is easily affected by the observation noise, so further measures need to be taken\cite{shen_shortterm2021}.
	A modified real-time Chow test approach was proposed for fast deformation monitoring\cite{bellone2016real}. This kind of method based on statistical index is easily affected by observation noise, and is not suitable for small displacement detection\cite{pirotti2015micro}. Besides, Dabove and Manzino\cite{dabove2016fast} introduced a cluster-based method for dynamic deformation analysis, but this method did not perform well on real data.

@@

	\subsubsection{Markov Chain Monte Carlo (MCMC)}
	The posterior distribution of the parameters depends on the prior distribution and the likelihood function. Obtaining the posterior probability of parameters by direct integration or sum requires a lot of operations, which is difficult to achieve\cite{robert2013monte}. In this work, the Markov chain Monte Carlo technique is used to approximate the integral or sum value. Monte Carlo sampling is to construct the integral or sum function as the expectation under a certain distribution, and then approximate the expectation by the corresponding average value\cite{goodfellow2016deep}.

	\begin{equation}\label{eq_monte_carlo_1}
	s =\sum\limits_x g(x)= \sum\limits_x {p(x)f(x) = {E_p}[f(x)]}
	\end{equation}
	\begin{equation}\label{eq_monte_carlo_2}
	s =\int {g(x)dx}= \int {p(x)f(x)dx}  = {E_p}[f(x)]
	\end{equation}
	where $g(x)$ is the function to be integrated or summated; $p(x)$ is the probability distribution or probability density function of $x$. The integral or summation problem of $g(x)$ is transformed into the mathematical expectation problem of $f(x)$ under the distribution $p(x)$. This mathematical expectation can be approximated by sampling from $p(x)$\cite{goodfellow2016deep}.

	\begin{equation}\label{eq_monte_carlo_3}
	\hat s = \frac{1}{n}\sum\limits_{i = 1}^n {f({x_i})}
	\end{equation}
	where $x_i$ is the sample with the distribution of $p(x)$. As can be seen from the above, Monte Carlo method as a general sampling simulation sum or integration method, depends on sampling from the distribution of $p(x)$. However, it is not easy to directly sample from the target distribution of $p(x)$. At present, the most popular solution is to use Markov chain Monte Carlo sampling, which provides a general way to construct a sequence that converges to the target distribution. According to Markov chain, the probability of state transition at a certain time only depends on its previous state, which is expressed as follows\cite{robert2013monte}

	\begin{equation}\label{eq_markov_chain_1}
	P({x_{n + 1}}\left| {{x_n},{x_{n - 1}}} \right.,{x_{n - 2}}, \cdots ,{x_2},{x_1}) = P({x_{n + 1}}\left| {{x_n}} \right.)
	\end{equation}
	If a Markov process is neither periodic nor irreducible, then the Markov process is ergodic, that is, each state appears with a certain probability. The Markov process of ergodic states has an important property: no matter what the initial state probability is, the Markov process of the ergodic state tends to be a stable distribution after enough state transitions\cite{robert2013monte}.
	That is, for the initial probability distribution is $\pi_0(x)$, the probability distribution after several rounds of state transition is as follows

	\begin{equation}\label{eq_markov_chain_2}
	\pi_{0}(x),\pi_{1}(x),\pi_{2}(x),\cdots \pi_{n}(x),\pi_{n+1}(x),\pi_{n+2}(x)\cdots
	\end{equation}
	There exists $n$ which satisfies the following conditions

	\begin{equation}\label{eq_markov_chain_3}
	\pi_{n}(x)=\pi_{n+1}(x)=\pi_{n+2}(x)\cdots
	\end{equation}
	This is the target distribution we want to construct. Based on the initial arbitrary simple probability distribution such as Gaussian distribution $\pi_{0}(x)$, the state value $x_0$ is obtained by sampling. Based on the probability distribution $\pi_{1}(x)=\pi_{0}(x)P(x\left| {{x_0}} \right.)$ sampling state value $x_1$, using the same method, execute $n$ times. Sample $(x_{n},x_{n+1},x_{n+2}\cdots)$ is the corresponding sample set of the target distribution. However, the implementation of MCMC also needs to consider other factors such as constructing the state transition matrix according to the target distribution\cite{robert2013monte}, which is beyond the scope of this work. Two implementations of MCMC,  the Metropolis-Hasting sampler\cite{chib1995understanding} and the No-U-Turn sampler\cite{hoffman2014no}, are used to sample discrete random variables and continuous random variables, respectively. Next, the data source of the proposed method: GNSS real-time kinematic positioning is introduced.

@@

	\subsubsection{Field Experiment 1}
	GNSS observations were processed epoch by epoch by using RTK mode, and the corresponding coordinate output was the only input of the proposed displacement detection method.
	The results of RTK positioning are shown in Fig. \ref{fig_v_bd9_3_up_tau}.
	Only the vertical displacement was triggered in the experiment, so only the up coordinate component is displayed. 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_ts}
		\caption{The up component of coordinates obtained by RTK positioning in field experiment 1.}
		\label{fig_v_bd9_3_up_ts}
	\end{figure}

	For such a short baseline, most of the errors can be eliminated by the double-difference observation. 
	As can be seen from Fig. \ref{fig_v_bd9_3_up_ts}, there are still some unmodeled errors, such as the multipath error that have not been eliminated. 
	The RTK positioning results are processed by the proposed method, and Bayesian inference is implemented by the MCMC sampling. 
	The histogram of the posterior sample of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau}.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_tau}
		\caption{Posterior sample distribution of $\tau$ in field experiment 1.}
		\label{fig_v_bd9_3_up_tau}
	\end{figure} 
	From the posterior sample distribution of $\tau_2$ in Fig. \ref{fig_v_bd9_3_up_tau}, one of the change points can be identified as 1897 s. 
	According to the maximum value in the bar chart of the posterior sample of $\tau_1$, the change point is identified as 781 s.
	However, as can be seen from Fig. \ref{fig_v_bd9_3_up_tau}, there are two peaks in the posterior sample distribution of change point $\tau_1$.
	The main reason is that the displacement control device is not completely controllable, and the plank floats up and down when moving the object. 
	In addition, since the antenna is close to the ground, the antenna vibration caused by breeze or touch causes an increase in the multipath phase rate or fading frequency\cite{kelly2003characterization}. 
	The index values of different index-based detection methods in field experiment 1 are shown in Fig. \ref{fig_v_exp1_idx}. At the abrupt point, each index value is no longer as clear as in the simulation experiment, which puts forward higher requirements for additional analysis of these indexes.
	The posterior sample histogram of the $\mu$ of each segment divided by the change point and the displacement measured by the tape are shown in Fig. \ref{fig_v_bd9_3_up_mu} and Table \ref{tab_measured_height_9_3}, respectively.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_exp1_idx}
		\caption{Index values of different index-based detection methods in field experiment 1.}
		\label{fig_v_exp1_idx}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_mu}
		\caption{Histogram of posterior sample of $\mu$ in field experiment 1.}
		\label{fig_v_bd9_3_up_mu}
	\end{figure} 
	\begin{table}[htbp]
		\centering
		%	\fontsize{6.5}{8}\selectfont
		\begin{threeparttable}
			\caption{Measured height before and after each movement of the object hanging on the plank in field experiment 1, unit (mm).}
			\label{tab_measured_height_9_3}
			\begin{tabular}{ccccccccc}
				\toprule
				&&&\textbf{1}&\textbf{2}&\textbf{3}&\textbf{4}&\textbf{5}&\textbf{mean}\cr
				\midrule
				\multirow{3}*{Step 1} 
				& & ${h_0}$    &371.0&370.9&370.9&371.1&370.9&370.96\\
				& & ${h_1}$    &341.0&341.1&341.5&341.9&341.0&341.30\\
				& & $\Delta h$ & -30.0& -29.8& -29.4& -29.2& -29.9&-29.66\\
				\hline
				\multirow{3}*{Step 2} 
				& & ${h_0}$    &340.5&340.1&340.0&340.0&340.1&340.14\\
				& & ${h_1}$    &313.0&312.9&312.9&313.0&313.0&312.96\\
				& & $\Delta h$ &-27.5& -27.2& -27.1& -27.0& -27.1& -27.18\\
				\bottomrule
			\end{tabular}
		\end{threeparttable}
	\end{table}

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_sigma}
		\caption{Histogram of posterior sample of $\sigma$ in field experiment 1.}
		\label{fig_v_bd9_3_up_sigma}
	\end{figure} 
	Different from the posterior sample distribution of $\tau$, there is only one peak value in the posterior sample distribution of $\mu$ and $\sigma$.
	The main reason is that the interval of the two peaks is very close, which has little influence on the posterior mean and standard deviation.
	In reality, multiple change points exist, such as multiple displacements in a short period of time in the process of landslide or settlement.
	However, more attention is paid to the primary change points.
	By adding a prior to the model to improve the identification of the primary change points, and weaken the influence of secondary change points will be discussed later.
	\subsubsection{Field Experiment 2}
	This experiment is similar to the previous one except that the displacement amplitude is smaller. 
	The coordinate time series is obtained by RTKLIB with the same processing strategy as the previous experiment, and the up component of the time series is shown in Fig. \ref{fig_v_bd9_4_up_ts}. 
	In this experiment, the displacement measured by tape is shown in Table \ref{tab_measured_height_9_4}.

	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_4_up_ts}
		\caption{The up component of coordinates obtained by RTK positioning in field experiment 2.}
		\label{fig_v_bd9_4_up_ts}
	\end{figure} 
	\begin{table}[h!t]
		\centering
		%	\fontsize{6.5}{8}\selectfont
		\begin{threeparttable}
			\caption{Measured height before and after each movement of the object hanging on the plank in field experiment 2, unit (mm).}
			\label{tab_measured_height_9_4}
			\begin{tabular}{ccccccccc}
				\toprule
				&&&\textbf{1}&\textbf{2}&\textbf{3}&\textbf{4}&\textbf{5}&\textbf{mean}\cr
				\midrule              
				\multirow{3}*{Step 1}
				& & ${h_0}$    &347.5&	347.3&	347.6&	347.5&	347.4&	347.5\\
				& & ${h_1}$    &326.1&	326.3&	326.1&	326.0&	326.1&	326.1\\
				& & $\Delta h$ &-21.4&	-21.0&	-21.5&	-21.5&	-21.3&	-21.3\\
				\hline               
				\multirow{3}*{Step 2}
				& & ${h_
					0}$    &325.0&	325.1&	324.9&	325.0&	325.2&	325.0\\
				& & ${h_1}$    &305.5&	305.3&	305.4&	305.5&	305.6&	305.5\\
				& & $\Delta h$ &-19.5&	-19.8&	-19.5&	-19.5&	-19.6&	-19.6\\
				\bottomrule
			\end{tabular}
		\end{threeparttable}
	\end{table}
	As can be seen from Fig. \ref{fig_v_bd9_4_up_ts} and Table \ref{tab_measured_height_9_4}, the amplitude of the two displacements is smaller than that of the previous experiment. 
	The time series are processed by the proposed method, and Bayesian inference is implemented by the MCMC sampling. The results are shown in Fig. \ref{fig_v_bd9_4_up_tau}, \ref{fig_v_bd9_4_up_mu}, and \ref{fig_v_bd9_4_up_sigma}.

>>>>

		\title{GNSS-based \textcolor{r_s}{Short-term} Displacement Detection Using Bayesian Inference for Deformation Monitoring}

@@

	\label{intro}
	%全球定位系统系统的应用-》位移探测
	%在自然灾害监测，或者工业测量等领域，GNSS被用于位移探测。
	%传统测量仪器的弊端，GNSS位移探测的优势。
	%GNSS在位移探测中扮演的角色，以及位移探测的要求
	%目前人们对于基于GNSS位移探测的研究更过的关注与如何提高定位的精度，而忽略了如何从GNSS获取的坐标序列中识别并提取位移。
	In recent decades, the Global navigation satellite system (GNSS) has been widely used in surveying, civil aviation, and autonomous vehicle as a positioning method\cite{barry2011surveying,iatsouk2004development}. 
	Besides, as a displacement detection method in deformation monitoring, GNSS has been widely applied to engineering fields such as landslide monitoring\cite{awange2012environmental}, subsidence survey\cite{bian2014monitoring}, industrial measurement\cite{pavasovic2011application}. 
	Displacement is an important parameter in engineering analysis in structural mechanics and geomechanics\cite{TASORA2020112635,BIGONI2020113315}.
	Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high precision, and weather independence\cite{shen2019a}. 
	%随着物联网通信技术标准的制订和创新，高精度定位技术，例如RTK，PPP，以及GNSS传输协议NTRIP的发展，GNSS定位结果可以被实时传输到云端。
	With the development of the Internet of things (IoT), GNSS high-precision positioning technology, and GNSS enhanced information transmission protocol, high-precision GNSS positioning results can be transmitted to the cloud in real-time.
	%Displacement detection involves displacement identification and extraction. 
	There are many researches on displacement detection based on GNSS, which can be divided into two categories.

@@

	\textcolor{r_s}{
	The other category is about displacement detection research based on GNSS.
	There are many studies on the use of high-rate GNSS for structure displacement extraction and parameter identification.
	Psimoulis et al.\cite{psimoulis2008_1,psimoulis2008_2} studied the feasibility of using GNSS for structural vibration detection. Experiments were carried out to evaluate the use of Global positioning system (GPS) to determine the parameters of oscillation of major structures.
	Meng et al.\cite{Meng_2018} presented the challenges faced by the design and implementation of a new monitoring system for large bridges. Damage detection in SHM of long-span bridges is very challenging because there is no general damage definition, and damage is usually unique and bridge-specific. Psimoulis et al.\cite{psimoulis2018detection} presented an algorithm named RT-SHAKE to detect ground motions, which aims to detect seismic motion more sensitively and robustly.	There are also studies on the relationship between receiver parameters and high-rate GNSS measurement\cite{Hberling2015,Moschas2015}.
	H{\"a}berling et al.\cite{Hberling2015} argued that due to the large error of dynamic GNSS measurement if high-rate GNSS is to be a valuable tool for seismic displacement measurement above 1 Hz, the baseband parameters of the GNSS receiver must be considered.
	Moschas et al.\cite{Moschas2015} studied the relationship between the phase-locked loop(PLL) bandwidth and noise in 100 Hz GPS measurement.
	The results show that the measurement correlation decreases with the increase of PLL bandwidth from low to high to 100 Hz. Shen et al.\cite{shennan_2019} gave a more detailed review of dynamic structural health monitoring technology based on GNSS. There are also studies on displacement detection such as landslide, and GNSS is usually used as a static positioning method.}
	Gili et al.\cite{gili2000using} was one of the first landslide monitoring studies using GNSS technology, in which traditional measurement data were used as a comparison. 
	The results showed that the accuracy of the GPS measurement over a period of 26 months was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
	A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\cite{rs12203375}. 
	The results of a nine-month of field monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement was obtained by the direct difference between the coordinates of the start and end periods.
	\textcolor{r_s}{
		Betti et al.\cite{betti2001deformation,betti2011deformation} studied the use of the Bayesian approach to evaluating deformation from GPS time series, in which a test procedure was constructed under the Bayesian framework. However, in this method, only specific epochs are tested, and how to identify these epochs is not involved.
		There are also some studies on the significance analysis of the GNSS control network based on the Bayesian test, and the control network processing results are generally based on repeated static adjustment.
	}

	%目前针对GNSS动态定位时间序列的位移识别和提取的研究还很少。目前研究都是基于长周期时间序列进行分析，对于动态定位结果分析的研究还是有限。
	%基于GNSS的位移监测通常是可以通过时域差分来完成
	%GNSS定位结果可以来源于重复的静态测量结果，重复测量周期一般为一天到几个月，这类叫监测被称作长周期监测。
	%另外，也可以利用实时定位结果进行探测，已获得实时或者近实时的探测结果，这类被称作短周期探测。
	\textcolor{r_s}{
	GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results\cite{abidin2004use,rs12203375}. The positioning results can be obtained from repeated GNSS static measurements, and the repetition period is generally one day to several months. This kind of displacement detection is called long-term displacement detection. In addition, real-time or near real-time detection can be obtained by using GNSS kinematic positioning results, which is called short-term detection.}
	At present, there are few studies on displacement identification and extraction of GNSS kinematic positioning time series. In \cite{li2010deformation}, a multiple Kalman filters model was proposed for deformation detection in the GPS real-time series. Different filters in the model represent different displacement models, which need to be defined in advance. 
	In addition, the index-based is also widely used, but it is easily affected by the observation noise, so further measures need to be taken\cite{shen_shortterm2021}.
	A modified real-time Chow test approach was proposed for fast deformation monitoring\cite{bellone2016real}. This kind of method based on statistical index is easily affected by observation noise, and is not suitable for small displacement detection\cite{pirotti2015micro}. Besides, Dabove and Manzino\cite{dabove2016fast} introduced a cluster-based method for dynamic deformation analysis, but this method did not perform well on real data.

@@

	\subsubsection{Markov Chain Monte Carlo (MCMC)}
	The posterior distribution of the parameters depends on the prior distribution and the likelihood function. Obtaining the posterior probability of parameters by direct integration or sum requires a lot of operations, which is difficult to achieve\cite{robert2013monte}. In this work, the Markov chain Monte Carlo technique is used to approximate the integral or sum value.  Two implementations of MCMC,  the Metropolis-Hasting sampler\cite{chib1995understanding} and the No-U-Turn sampler\cite{hoffman2014no}, are used to sample discrete random variables and continuous random variables, respectively. Next, the data source of the proposed method: GNSS real-time kinematic positioning is introduced.

@@

	\subsubsection{Field Experiment 1}%rover_bd9_3
	GNSS observations were processed epoch by epoch by using RTK mode, and the corresponding coordinate output was the only input of the proposed displacement detection method.
	The results of RTK positioning are shown in Fig. \ref{fig_v_bd9_3_up_tau}.
	Only the vertical displacement was triggered in the experiment, so only the up coordinate component is displayed. 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_ts}
		\caption{The up component of coordinates obtained by RTK positioning in field experiment 1.}
		\label{fig_v_bd9_3_up_ts}
	\end{figure}

	For such a short baseline, most of the errors can be eliminated by the double-difference observation. 
	As can be seen from Fig. \ref{fig_v_bd9_3_up_ts}, there are still some unmodeled errors, such as the multipath error that have not been eliminated. 
	The RTK positioning results are processed by the proposed method, and Bayesian inference is implemented by the MCMC sampling. 
	The histogram of the posterior sample of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau}.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_tau}
		\caption{Posterior sample distribution of $\tau$ in field experiment 1.}
		\label{fig_v_bd9_3_up_tau}
	\end{figure} 
	From the posterior sample distribution of $\tau_2$ in Fig. \ref{fig_v_bd9_3_up_tau}, one of the change points can be identified as 1897 s. 
	According to the maximum value in the bar chart of the posterior sample of $\tau_1$, the change point is identified as 781 s.
	However, as can be seen from Fig. \ref{fig_v_bd9_3_up_tau}, there are two peaks in the posterior sample distribution of change point $\tau_1$.
	The main reason is that the displacement control device is not completely controllable, and the plank floats up and down when moving the object. 
	In addition, since the antenna is close to the ground, the antenna vibration caused by breeze or touch causes an increase in the multipath phase rate or fading frequency\cite{kelly2003characterization}. 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{ndop_snrmp_9_3}
		\caption{Number of satellites, GDOP, SNR, multipath of experiment 1.}
		\label{fig_v_ndop_snrmp_9_3}
	\end{figure} 
	The index values of different index-based detection methods in field experiment 1 are shown in Fig. \ref{fig_v_exp1_idx}. At the abrupt point, each index value is no longer as clear as in the simulation experiment, which puts forward higher requirements for additional analysis of these indexes.
	The posterior sample histogram of the $\mu$ of each segment divided by the change point and the displacement measured by the tape are shown in Fig. \ref{fig_v_bd9_3_up_mu} and Table \ref{tab_measured_height_9_3}, respectively.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_exp1_idx}
		\caption{Index values of different index-based detection methods in field experiment 1.}
		\label{fig_v_exp1_idx}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_mu}
		\caption{Histogram of posterior sample of $\mu$ in field experiment 1.}
		\label{fig_v_bd9_3_up_mu}
	\end{figure} 
	\begin{table}[htbp]
		\centering
		%	\fontsize{6.5}{8}\selectfont
		\begin{threeparttable}
			\caption{Measured height before and after each movement of the object hanging on the plank in field experiment 1, unit (mm).}
			\label{tab_measured_height_9_3}
			\begin{tabular}{ccccccccc}
				\toprule
				&&&\textbf{1}&\textbf{2}&\textbf{3}&\textbf{4}&\textbf{5}&\textbf{mean}\cr
				\midrule
				\multirow{3}*{Step 1} 
				& & ${h_0}$    &371.0&370.9&370.9&371.1&370.9&370.96\\
				& & ${h_1}$    &341.0&341.1&341.5&341.9&341.0&341.30\\
				& & $\Delta h$ & -30.0& -29.8& -29.4& -29.2& -29.9&-29.66\\
				\hline
				\multirow{3}*{Step 2} 
				& & ${h_0}$    &340.5&340.1&340.0&340.0&340.1&340.14\\
				& & ${h_1}$    &313.0&312.9&312.9&313.0&313.0&312.96\\
				& & $\Delta h$ &-27.5& -27.2& -27.1& -27.0& -27.1& -27.18\\
				\bottomrule
			\end{tabular}
		\end{threeparttable}
	\end{table}

@@

	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_sigma}
		\caption{Histogram of posterior sample of $\sigma$ in field experiment 1.}
		\label{fig_v_bd9_3_up_sigma}
	\end{figure} 
	Different from the posterior sample distribution of $\tau$, there is only one peak value in the posterior sample distribution of $\mu$ and $\sigma$.
	The main reason is that the interval of the two peaks is very close, which has little influence on the posterior mean and standard deviation.
	In reality, multiple change points exist, such as multiple displacements in a short period of time in the process of landslide or settlement.
	However, more attention is paid to the primary change points.
	By adding a prior to the model to improve the identification of the primary change points, and weaken the influence of secondary change points will be discussed later.
	\subsubsection{Field Experiment 2}%rover_bd9_4 part(650)
	This experiment is similar to the previous one except that the displacement amplitude is smaller. 
	The coordinate time series is obtained by RTKLIB with the same processing strategy as the previous experiment, and the up component of the time series is shown in Fig. \ref{fig_v_bd9_4_up_ts}. 
	In this experiment, the displacement measured by tape is shown in Table \ref{tab_measured_height_9_4}.

	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_4_up_ts}
		\caption{The up component of coordinates obtained by RTK positioning in field experiment 2.}
		\label{fig_v_bd9_4_up_ts}
	\end{figure} 
	\begin{table}[h!t]
		\centering
		%	\fontsize{6.5}{8}\selectfont
		\begin{threeparttable}
			\caption{Measured height before and after each movement of the object hanging on the plank in field experiment 2, unit (mm).}
			\label{tab_measured_height_9_4}
			\begin{tabular}{ccccccccc}
				\toprule
				&&&\textbf{1}&\textbf{2}&\textbf{3}&\textbf{4}&\textbf{5}&\textbf{mean}\cr
				\midrule              
				\multirow{3}*{Step 1}
				& & ${h_0}$    &347.5&	347.3&	347.6&	347.5&	347.4&	347.5\\
				& & ${h_1}$    &326.1&	326.3&	326.1&	326.0&	326.1&	326.1\\
				& & $\Delta h$ &-21.4&	-21.0&	-21.5&	-21.5&	-21.3&	-21.3\\
				\hline               
				\multirow{3}*{Step 2}
				& & ${h_
					0}$    &325.0&	325.1&	324.9&	325.0&	325.2&	325.0\\
				& & ${h_1}$    &305.5&	305.3&	305.4&	305.5&	305.6&	305.5\\
				& & $\Delta h$ &-19.5&	-19.8&	-19.5&	-19.5&	-19.6&	-19.6\\
				\bottomrule
			\end{tabular}
		\end{threeparttable}
	\end{table}

	\begin{figure}[htbp]
	\centering
	\includegraphics[scale=0.45]{ndop_snrmp_9_4}
	\caption{Number of satellites, GDOP, SNR, multipath of experiment 2.}
	\label{fig_v_ndop_snrmp_9_4}
	\end{figure} 
	As can be seen from Fig. \ref{fig_v_bd9_4_up_ts} and Table \ref{tab_measured_height_9_4}, the amplitude of the two displacements is smaller than that of the previous experiment. 
	The time series are processed by the proposed method, and Bayesian inference is implemented by the MCMC sampling. The results are shown in Fig. \ref{fig_v_bd9_4_up_tau}, \ref{fig_v_bd9_4_up_mu}, and \ref{fig_v_bd9_4_up_sigma}.
